---
title: "Smart_Beta"
author: "Anshul Singhal"
date: "10/19/2021"
output: github_document
---

```{r setup, include=FALSE} 
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```


###Loading the Packages which are required
```{r include = FALSE}
library(dplyr)
require(data.table)
library(haven)
library(zeallot)
library(lubridate)
library(plotly)
library(openxlsx)
library(readxl)
library(zoo)
library(scales)
library(geckor)
library(fredr)
library(tidyquant)
library(tidyr)
library(naniar)
library(tidyverse)
library(forestmangr)
library(tibbletime)
library(lmtest)
library(sandwich)
library(shiny)
library(plotly)
fredr_set_key("669c24e3e2c8136b6db6b3c978104993")
```

###Functions Used in the Code
```{r}
#Some of the functions are taken from the previous assignments

rolling_function = function(x,y,z,col_name){
  if(col_name == "roll_beta"){
      rolling <- rollify(function(x, y) {
                         cov(x,y)/var(y)
                       },
                       window = z)
      return(rolling(x,y))
  }
  else if(col_name == "annualised_vol"){
      rolling <- rollify(function(x) {
                       sd(x)*sqrt(12)
                       },
                       window = z)
  }
  else{
      rolling <- rollify(function(x) {
                   sqrt(sum(x**2))
                   },
                   window = z)
  }
  return(rolling(x))
}


#monthly beta calculation function
rolling_calculation = function(data,window,col_name){
  
  stock_data_modified = data%>%
  group_by(CUSIP)%>%
  filter(n() >= window)%>%
  arrange(DATE_START)%>%
  mutate(!!col_name := lag(rolling_function(RET,VWRETD,window,!!col_name)))%>%
  group_by(DATE_START)%>% 
  filter(month(DATE_START)==1)%>%
  drop_na(sym(col_name))
  
  return(stock_data_modified)
}

"Descriptive Stats Function :std,skewness,kurtosis, sharpe and information ratio"
stats = function(dat){
std_group = dat %>%
  summarise(across(everything(), sd,na.rm = TRUE,.names = "std_{.col}"))
skewness_group = dat %>%
  summarise(across(everything(), skewness, na.rm = TRUE,.names = "skew_{.col}"))
kurtosis_group = dat %>%
  summarise(across(everything(),kurtosis, na.rm = TRUE,.names = "kurt_{.col}"))
sharpe_group = dat %>%
  summarise(across(everything(), mean,na.rm = TRUE,.names = "sharpe_{.col}"))
sharpe_group = sharpe_group/std_group
dat = dat %>%
    mutate_at(vars(-matches("market_cum_return")), ~ . - market_cum_return)
information_group = dat %>%
  summarise(across(everything(), mean,na.rm = TRUE,.names = "information_{.col}"))
information_group_sd = dat %>%
  summarise(across(everything(), sd,na.rm = TRUE,.names = "information_sd_{.col}"))
information_group = information_group/information_group_sd
 return (list(std_group,skewness_group,kurtosis_group,sharpe_group,information_group))
}

#Adapted directly from Jonathan Regenstein R Session 3 Code
recession_shade_fun <- function(color_chosen = "darkgray",
                                start_date = "1970-01-01"){
  "USREC" %>%
  tq_get(get = "economic.data", from = start_date) %>%
  rename(year = date)%>%
  select(year, recession_flag = price) %>%
  mutate(recession_label = case_when(recession_flag == 1 & lag(recession_flag == 0) ~ str_glue("{year(year)} recession"),
         TRUE ~ NA_character_)) %>%
  filter(recession_flag == 1) %>%
  fill(recession_label, .direction = "down") %>%
  group_by(recession_label) %>%
  slice(1, n()) %>%
  select(-recession_flag) %>%
  mutate(start = case_when(year == min(year) ~ year,
                           TRUE ~ NA_Date_),
         end = case_when(year == max(year) ~ year,
                         TRUE ~ NA_Date_),
         end = lead(end)
         ) %>%
  filter(!is.na(start)) %>%
  select(-year) %>%
    geom_rect(data = .,
            inherit.aes = F,
            aes(xmin = start,
                xmax = end,
                ymin = -Inf,
                ymax = +Inf),
            fill = color_chosen,
            alpha = 0.4)
}

#
plot_data = function(data, datatype) {
  df <- melt(data ,  id.vars = 'year', variable.name = 'Portfolio')
  df = df%>%
    rename(Returns = value)%>%
    drop_na(Returns)
ggplot(df, aes(x = year, y = Returns, colour = Portfolio)) +
  geom_line()+ recession_shade_fun() +theme_minimal()+
  ggtitle(datatype)+ theme(plot.title = element_text(hjust = 0.5))
  
}

#Regression Beta and RSE Calculation
beta_calculation = function(data,frequency,col_name,indepVars = c("VWRETD"),start_index_depVars = 3){
  value = "value"
  regression_data_1 = data%>%
  mutate(value = floor_date(DATE_START, unit = frequency))%>%
  select(-c(DATE_START))%>%
  drop_na(RET)%>%
  pivot_wider(names_from = CUSIP, values_from = c(RET),values_fill = 0)%>%
  arrange(value)

  names(regression_data_1) = c(indepVars,value,paste0("CUSIP_",colnames(regression_data_1[start_index_depVars:ncol(regression_data_1)])))

  depVars <- paste(c(colnames(regression_data_1[start_index_depVars:ncol(regression_data_1)])))

  models = regression_data_1 %>%
    group_by(value) %>%
    do(model = list(lm(formula(paste('cbind(',
                   paste(depVars, collapse = ','),
                   ') ~ ',
                   paste(indepVars, collapse = '+'))),na.action = na.exclude ,data = .)))
  if(start_index_depVars >= 3)
  {
    mkt_beta = list(models$model[1][[1]][[1]]$coefficients[2,])
  }
  if(start_index_depVars >= 5)
  {
    smb_beta = list(models$model[1][[1]][[1]]$coefficients[3,])
    hml_beta = list(models$model[1][[1]][[1]]$coefficients[4,])
  }
  if(start_index_depVars >= 6){
    mom_beta = list(models$model[1][[1]][[1]]$coefficients[5,])
  }
  k = models$model[1][[1]][[1]]$residuals
  k1 = list(t(sqrt(colSums(k**2)*12/(12-length(indepVars)-1))))
  for (i in 2:nrow(models)){
    if(start_index_depVars >= 3){
      mkt_beta = append(mkt_beta,list(models$model[i][[1]][[1]]$coefficients[2,]))
    }
    if(start_index_depVars >= 5){
      smb_beta = append(smb_beta,list(models$model[i][[1]][[1]]$coefficients[3,]))
      hml_beta = append(hml_beta,list(models$model[i][[1]][[1]]$coefficients[4,]))
    }
    if(start_index_depVars >= 6){
      mom_beta = append(mom_beta,list(models$model[i][[1]][[1]]$coefficients[5,]))
      
    }
    k = models$model[i][[1]][[1]]$residuals
    k1 = append(k1,list(t(sqrt(colSums(k**2)*12/(12-length(indepVars)-1)))))
    
  }
  a = list()
  if(start_index_depVars >= 3){
    mkt_beta  = as.tibble(do.call(rbind, mkt_beta))
    mkt_beta = cbind(models$value,mkt_beta)
    mkt_beta <- mkt_beta %>%
      tibble()%>%
      rename(value = "models$value")
    names(mkt_beta)[1] = col_name
    a = c(a,list(mkt_beta))
      
  }
  if(start_index_depVars >= 5){
    smb_beta  = as.tibble(do.call(rbind, smb_beta))
    smb_beta = cbind(models$value,smb_beta)
    smb_beta <- smb_beta %>%
      tibble()%>%
      rename(value = "models$value")
    names(smb_beta)[1] = col_name
    hml_beta  = as.tibble(do.call(rbind, hml_beta))
    hml_beta = cbind(models$value,hml_beta) 
    hml_beta <- hml_beta %>%
      tibble()%>%
      rename(value = "models$value")
    names(hml_beta)[1] = col_name
    a = c(a,list(smb_beta),list(hml_beta))
    
  }
  if(start_index_depVars >= 6){
    mom_beta  = as.tibble(do.call(rbind, mom_beta))
    mom_beta = cbind(models$value,mom_beta) 
    mom_beta <- mom_beta %>%
      tibble()%>%
      rename(value = "models$value")
    names(mom_beta)[1] = col_name
    a = c(a,list(mom_beta))

  }

  rse = as.tibble(do.call(rbind, k1))
  rse = cbind(models$value,rse)

  rse <- rse %>%
    tibble()%>%
    rename(value = "models$value")
  
  names(rse)[1] = col_name
  return(list(a,rse))
}

#Cumulate the returns code yearly
agg_Returns <- function(year_return) {

  agg_return <- year_return %>%
              group_by(pent_ranks) %>%
              mutate(Eq_cum_returns = cumprod(1+Eq_yearly_returns)-1,
                     Wtd_cum_return = cumprod(1+Weighted_yearly_returns)-1,
                     market_cum_return = cumprod(1+mkt_returns)-1) %>%
              select(c(year, pent_ranks,Eq_cum_returns, Wtd_cum_return)) %>%
              ungroup()%>%
              inner_join(benchmarks_yearly)
}

#Yearly Returns without cumulation(Only cumulated on monthly basis to base year)
net_Returns <- function(year_return) {

  net_return <- year_return %>%
              group_by(pent_ranks) %>%
              mutate(Eq_cum_returns = Eq_yearly_returns,
                     Wtd_cum_return = Weighted_yearly_returns,
                     market_cum_return = mkt_returns) %>%
              select(c(year, pent_ranks,Eq_cum_returns, Wtd_cum_return,market_cum_return))%>%
              ungroup()
}

#Portfolio Returns Calculation
portfolio_returns <- function(year_ranked, variable_name) {
  
  yearly_portfolio_returns <- year_ranked %>% 
              drop_na(pent_ranks) %>%
              select(c("year", "CUSIP", "cum_excess_return", "market_cum_return", variable_name, "pent_ranks")) %>%
              group_by(year, pent_ranks) %>%
              summarise(Eq_yearly_returns = mean(cum_excess_return,na.rm=TRUE),
                        mkt_returns = mean(market_cum_return, na.rm=TRUE),
                        Weighted_yearly_returns = weighted.mean(cum_excess_return,!!sym(variable_name), na.rm = TRUE)) %>%
              ungroup()
}

#Final Portfolio calling all the above function
#Taking 5 Portfolios based on 20% quantiles
calculatePortfolio <- function(funda_saved_1, yearly_returns, variable_name) {
  ranking_sec <- funda_saved_1 %>%
            drop_na(variable_name) %>%
            mutate(fyear = as.Date(paste(fyear, 1, 1, sep = "-"))) %>% 
            group_by(fyear) %>%
            mutate(pent_ranks = ntile(!!sym(variable_name),5))
    
  yearly_data_ranked <- yearly_returns %>%
              inner_join(ranking_sec,  by = c("year" = "fyear", "CUSIP" = "cusip")) %>%
              drop_na(pent_ranks) 
  
  returns_1 <- yearly_data_ranked %>%
                portfolio_returns(variable_name)
  agg_returns = returns_1%>%
                drop_na()%>%
                agg_Returns()
  normal_returns = returns_1 %>%
                net_Returns()

  agg_returns <- agg_returns %>% select(-c(Eq_cum_returns)) %>% pivot_wider(names_from = pent_ranks, values_from = Wtd_cum_return)
print(plot_data(agg_returns, paste(variable_name, " Portfolios")))
normal_returns = normal_returns %>% select(-c(Eq_cum_returns)) %>% pivot_wider(names_from = pent_ranks, values_from = Wtd_cum_return)

return (list(normal_returns,agg_returns))

}

```

###Loading the COMPUSTAT Data
```{r}
path_funda = "D:/anshul stuffs/gatech/material/MFI_Assignment/Assignment_4/"

variables = read.csv(paste0(path_funda,"Variable_Names.csv"))
variables$lower = tolower(variables$Variable_Name)
variable_list = unique(variables$lower)

col_list = c("gvkey","fyear","indfmt","tic","conm","scf","compst","sich","cusip","revt",variable_list)
fundamental_data = read_sas(paste0(path_funda,"funda.sas7bdat"),col_select = col_list)


fundamental_data <- fundamental_data%>%
                  filter(compst != "AB") %>%   
                  filter (scf != 4, scf != 5, scf != 6) %>%
                  drop_na(scf, at) %>%
                  filter(at != 0) %>% 
                  select(-c(compst,sich)) 

```

###Creating the variables out of the Fundamentals
```{r}
"Creating the fundamental variables using the COMPUSTAT Data ang lagging the variables"
fundamental_data[is.na(fundamental_data)] =  0
fundamental_vars_to_save <- c('fyear','cusip','mkvalt','conm','book_val', 'cashflows_trailing', 'revt_trailing','sale_trailing','div_trailing','investment_trailing','prof_trailing','asset_turnover')

fundamental_data_to_save <- fundamental_data %>%
                    arrange(fyear) %>%
                    group_by(cusip) %>%
                    mutate(book_val = lag(at-dlc-dltt),
                          investments = lag(ifelse(scf %in% c(1:3), 
                          capx+ivch+aqc+fuseo-sppe-siv,
                          capx+ivch+aqc-sppe-siv-ivstch-ivaco)),
                          net_cashflow = lag(fincf + ivncf + oancf),
                          avg_at =  (at + ifelse(!is.na(lag(at)),lag(at),at))/2, 
                          roa = lag(oiadp/avg_at)) %>%
                    drop_na(investments,net_cashflow,revt,sale,dv,roa) %>%
                    mutate(cashflows_trailing = rollapplyr(net_cashflow, 5, mean, na.rm = TRUE, fill = NA),
                        revt_trailing = rollapplyr(lag(revt), 5, mean, na.rm = TRUE, fill = NA),
                        sale_trailing = rollapplyr(lag(sale), 5, mean, na.rm = TRUE, fill = NA),
                        div_trailing = rollapplyr(lag(dv), 5, mean, na.rm = TRUE, fill = NA),
                        investment_trailing = rollapplyr(investments,5, mean, na.rm = TRUE, fill = NA),
                        prof_trailing = rollapplyr(roa, 5, mean, na.rm = TRUE, fill = NA),
                        asset_turnover = lag(sale/avg_at)) %>%
                    select(fundamental_vars_to_save)

#Remove the variables from the environment and storing the dataset in the environment so, that if we have to use them later, it can be used without keeping the variables in the memory. Also, collecting the garbage collector(gc)
write.csv(fundamental_data_to_save, "fundamental_saved.csv")
rm(fundamental_data_to_save)
rm(fundamental_data)
gc()

```

###Reading the CRSP Data (Monthly)
```{r}
###Reading the Monthly Data 

path = "D:/anshul stuffs/gatech/material/MFI_Assignment/Assignment_5/"
monthly_data = fread(paste0(path,"msf_new2.csv"))
monthly_data = monthly_data%>%
  tibble()


```
###Modifying the Monthly Data
```{r}
###Modifying the Monthly Data and mapping Industry

#Parsing the dates
monthly_data_modified = monthly_data%>%
  arrange(CUSIP,DATE)%>%
  drop_na(PRC)%>%
  mutate(PRC = abs(PRC))%>%
  filter(SHRCD %in% c(10,11))%>%
  select(c(CUSIP,DATE,PRC,RET,VOL,SHROUT,VWRETD,SHRCD))%>%
  mutate(DATE = as.Date(parse_date_time(DATE, orders = "Ymd")),MKTCAP = abs(PRC*SHROUT),DATE_START = floor_date(DATE, unit = "month"))%>%
  mutate(across(c(RET),as.numeric))%>%
  group_by(CUSIP)%>%
  mutate(RET = PRC/lag(PRC)-1)%>%
  distinct(DATE,.keep_all = TRUE)%>%
  ungroup()

rm(monthly_data)
gc()

```


###Fama French Extract RF Monthly
```{r}
"Extracting the Risk Free Rate and calculating the Excess Return and Risk Premium"

#Reading the Momentum and Fama French Data and joining both with the CRSP Data
risk_free_data = read.csv(paste0(path,"F-F_Research_Data_Factors.csv"),skip = 2)
names(risk_free_data)[1] = "DATE_START"
risk_free_data = risk_free_data%>%
  tibble()%>%
  mutate(DATE_START = as.Date(parse_date_time(DATE_START, orders = "Ym")))%>%
  drop_na(DATE_START)%>%
  mutate_if(is.character, as.numeric)

mom_data = read.csv("F-F_Momentum_Factor.csv",skip = 12)
names(mom_data)[1] = "DATE_START"
mom_data = mom_data%>%
  tibble()%>%
  mutate(DATE_START = as.Date(parse_date_time(DATE_START, orders = "Ym")))%>%
  drop_na(DATE_START)%>%
  mutate_if(is.character, as.numeric)

risk_free_data = risk_free_data%>%
  merge(mom_data,by = "DATE_START")

risk_free_data[,2:ncol(risk_free_data)] = risk_free_data[,2:ncol(risk_free_data)]/100

monthly_data_modified_risk_free = monthly_data_modified%>%
  tibble()%>%
  merge(risk_free_data,by = "DATE_START")%>%
  drop_na(RET)%>%
  arrange(CUSIP,DATE_START)

monthly_data_modified_risk_free = monthly_data_modified_risk_free%>%
  mutate(MKT = Mkt.RF+RF)%>%
  select(-c(Mkt.RF))


stock_data = monthly_data_modified_risk_free%>%
  select(DATE_START,CUSIP,RET,VWRETD)

#calculating the rolling beta, yearly vol and vol squared for 12M
beta_yearly = rolling_calculation(stock_data,12,"roll_beta")
vol_yearly = rolling_calculation(stock_data,12,"annualised_vol")
vol_yearly_squared = rolling_calculation(stock_data,12,"annualised_vol_squared")

rm(monthly_data_modified)
gc()
```

###Betas and RSE Calculation for the Regression
```{r}
"Creating the Beta, RSE using CAPM, Fama French 3 Factor and 4 Factor Model "

c(betas_capm,rse_market_capm) %<-% beta_calculation((monthly_data_modified_risk_free%>%
  select(DATE_START,CUSIP,RET,VWRETD)),"12month","YEAR_START")
beta_market_capm = betas_capm[[1]]

c(betas_ff3,rse_market_ff3) %<-% beta_calculation((monthly_data_modified_risk_free%>%
  select(DATE_START,CUSIP,RET,SMB,HML,VWRETD)),"12month","YEAR_START",c("VWRETD","SMB","HML"),5)
c(beta_market_ff3,beta_smb_ff3,beta_hml_ff3) %<-% betas_ff3


c(betas_ff4,rse_market_ff4) %<-% beta_calculation((monthly_data_modified_risk_free%>%
  select(DATE_START,CUSIP,RET,SMB,HML,VWRETD,Mom)),"12month","YEAR_START",c("VWRETD","SMB","HML","Mom"),6)

c(beta_market_ff4,beta_smb_ff4,beta_hml_ff4,beta_mom_ff4) %<-% betas_ff4

gc()

```

### Analysis for the monthly data
```{r}

"Adding the microstructure in the stock"
#Using the CPI Deflator to scale the companies at current dollar value of $100M, which is used at the time of filtering stocks based on the suggested microstructure.
cpi_deflator <- 
   "CPIAUCNS" %>% 
        tq_get(get = "economic.data", from = "1925-01-01") %>% 
        select(DATE_START = date, INDEX  =  price) %>%
        mutate(MULT = INDEX[DATE_START == "2021-06-01"]/INDEX,
               fyear = year(DATE_START))

monthly_data <- fread(paste0(path,"msf_new2.csv")) %>% tibble()

monthly_data <- monthly_data %>%
              mutate(RET = as.numeric(RET)) %>%
              drop_na(RET) %>%
              filter (SHRCD %in% c(10,11), DATE > 19700000) %>%
              mutate(DATE_START = as.Date(parse_date_time(DATE, orders = "Ymd")),
                     DATE_START = floor_date(DATE_START, unit = "month"),
                     PRC = ABS(PRC)) %>%
              inner_join(risk_free_data) %>%
              mutate(excess_return = RET - RF,
                     mkt_excess_return = VWRETD -RF,
                     year = year(DATE_START))

# Lag data monthly by 1 
monthly_data <- monthly_data %>%
              arrange(DATE_START) %>%
              group_by(CUSIP) %>%
              mutate(excess_return = lag(excess_return),
                     mkt_excess_return = lag(mkt_excess_return))

year_returns <- monthly_data %>%
              ungroup() %>%
              group_by(CUSIP,year) %>%
              mutate(year = as.Date(paste(year, 1, 1, sep = "-"))) %>% 
              summarise(market_cum_return = prod(1+mkt_excess_return)-1,
                        cum_excess_return = prod(1+excess_return)-1)


#Cusips filter for joining
cusips_to_filter <- monthly_data %>%
                inner_join(cpi_deflator) %>%
                mutate(mkt_cap_deflated = PRC*SHROUT*MULT,
                       price_deflated = PRC*MULT) %>%
                filter(mkt_cap_deflated < 100000000,
                       price_deflated > 4) %>%
                select(CUSIP) %>%
                rename(cusip = CUSIP) %>%
                unique()

#Saving the fundamental data which can be read later to save the memory
funda_saved <- fread("fundamental_saved.csv",header = T) %>% 
                  tibble() %>% 
                  mutate(cusip = str_sub(cusip,1,8)) %>%
                  filter(fyear >= 1970)

funda_filtered <- funda_saved %>%
                  inner_join(cusips_to_filter) 

#Yearly benchmarks created to be compared later with the portfolio 
benchmarks_yearly <- risk_free_data %>%
              mutate(DATE_START = as.Date(paste(year(DATE_START), 1, 1, sep = "-"))) %>%
              group_by(DATE_START) %>%
              summarise(mkt_french_returns = prod(1+`Mkt.RF`)-1,
                        smb_yearly = prod(1 + SMB)-1,
                        hml_yearly = prod(1 + HML)-1) %>% 
              filter(year(DATE_START) > 1970) %>%
              mutate(market_cum_return = cumprod(1 + mkt_french_returns) - 1,
                     smb_cum_return = cumprod(1 + smb_yearly) - 1,
                     hml_cum_return = cumprod(1 + hml_yearly)-1) %>%
              rename(year = DATE_START)%>%
              select(c(year, market_cum_return, smb_cum_return, hml_cum_return,mkt_french_returns))
rm(monthly_data)
gc()
                
```

### Fundamental Variables Indexing - Portfolio Construction
```{r}

c(normal_returns_book_val,cum_returns_book_val) %<-% calculatePortfolio(funda_filtered,year_returns , "book_val")

c(normal_returns_cf,cum_returns_cf) %<-% calculatePortfolio(funda_filtered%>% filter(cashflows_trailing != 0),year_returns, "cashflows_trailing")

c(normal_returns_rev,cum_returns_rev) %<-% calculatePortfolio(funda_filtered, year_returns, "revt_trailing")
  
c(normal_returns_sale,cum_returns_sale) %<-% calculatePortfolio(funda_filtered, year_returns, "sale_trailing")

c(normal_returns_div,cum_returns_div) %<-% calculatePortfolio(funda_filtered, year_returns, "div_trailing")

c(normal_returns_inv,cum_returns_inv) %<-% calculatePortfolio(funda_filtered, year_returns, "investment_trailing")

c(normal_returns_prof,cum_returns_prof) %<-% calculatePortfolio(funda_filtered, year_returns, "prof_trailing")

c(normal_returns_asset,cum_returns_asset) %<-% calculatePortfolio(funda_filtered, year_returns, "asset_turnover")

#Stats for the fundamentals
stats(normal_returns_book_val%>%select(-c(year)))
stats(normal_returns_cf%>%select(-c(year)))
stats(normal_returns_rev%>%select(-c(year)))
stats(normal_returns_sale%>%select(-c(year)))
stats(normal_returns_div%>%select(-c(year)))
stats(normal_returns_inv%>%select(-c(year)))
stats(normal_returns_prof%>%select(-c(year)))
stats(normal_returns_asset%>%select(-c(year)))
gc()
```

###Market Variables based Indexing
```{r}
#Market Variables calculation
beta_market_capm_longer <- beta_market_capm %>% pivot_longer(!YEAR_START,names_to = "CUSIP",values_to = "regression_beta") %>% rename(DATE_START = YEAR_START) %>%
   mutate(CUSIP = str_remove(CUSIP,"CUSIP_"))
joined_data_beta <- beta_market_capm_longer%>% merge(beta_yearly,by = c("DATE_START","CUSIP"))

rse_market_capm_long <- rse_market_capm %>% pivot_longer(!YEAR_START,names_to = "CUSIP",values_to = "IdioSyncratic_Vol_CAPM") %>% rename(DATE_START = YEAR_START) %>%
   mutate(CUSIP = str_remove(CUSIP,"CUSIP_"))
joined_data_beta <- rse_market_capm_long%>% merge(joined_data_beta,by = c("DATE_START","CUSIP"))

rse_ff3_long <- rse_market_ff3 %>% pivot_longer(!YEAR_START,names_to = "CUSIP",values_to = "IdioSyncratic_Vol_FF3_Model") %>% rename(DATE_START = YEAR_START) %>%
   mutate(CUSIP = str_remove(CUSIP,"CUSIP_"))
joined_data_beta <- rse_ff3_long%>% merge(joined_data_beta,by = c("DATE_START","CUSIP"))

rse_ff4_long <- rse_market_ff4 %>% pivot_longer(!YEAR_START,names_to = "CUSIP",values_to = "IdioSyncratic_Vol_FF4_Model") %>% rename(DATE_START = YEAR_START) %>%
   mutate(CUSIP = str_remove(CUSIP,"CUSIP_"))
joined_data_beta <- rse_ff4_long%>% merge(joined_data_beta,by = c("DATE_START","CUSIP"))


#Portfolio Returns Calculation
c(normal_returns_beta_yearly,cum_returns_beta_yearly) %<-% calculatePortfolio(beta_yearly %>% rename(fyear = DATE_START, cusip = CUSIP), year_returns, "roll_beta")

c(normal_returns_annualised_vol_yearly,cum_returns_annualised_vol_yearly) %<-% calculatePortfolio(vol_yearly %>% rename(fyear = DATE_START, cusip = CUSIP), year_returns, "annualised_vol")

c(normal_returns_annualised_vol_yearly_squared,cum_returns_annualised_vol_yearly_squared) %<-% calculatePortfolio(vol_yearly_squared %>% rename(fyear = DATE_START, cusip = CUSIP), year_returns, "annualised_vol_squared")

c(normal_returns_vol_capm,cum_returns_vol_capm) %<-% calculatePortfolio(joined_data_beta %>% rename(fyear = DATE_START, cusip = CUSIP), year_returns, "IdioSyncratic_Vol_CAPM")

c(normal_returns_vol_ff3,cum_returns_vol_ff3) %<-% calculatePortfolio(joined_data_beta %>% rename(fyear = DATE_START, cusip = CUSIP), year_returns, "IdioSyncratic_Vol_FF3_Model")

c(normal_returns_vol_ff4,cum_returns_vol_ff4) %<-% calculatePortfolio(joined_data_beta %>% rename(fyear = DATE_START, cusip = CUSIP), year_returns, "IdioSyncratic_Vol_FF4_Model")


#Calculation of stats
stats(normal_returns_beta_yearly%>%select(-c(year)))
stats(normal_returns_annualised_vol_yearly%>%select(-c(year)))
stats(normal_returns_annualised_vol_yearly_squared%>%select(-c(year)))
stats(normal_returns_vol_capm%>%select(-c(year)))
stats(normal_returns_vol_ff3%>%select(-c(year)))
stats(normal_returns_vol_ff4%>%select(-c(year)))

#For joining the data to for feedig the data to Shiny
y_dim = ncol(cum_returns_beta_yearly)
names(cum_returns_beta_yearly)[6:y_dim] = c(paste0(colnames(cum_returns_beta_yearly[6:y_dim]),"_Beta_Yearly"))

names(cum_returns_annualised_vol_yearly)[6:y_dim] = c(paste0(colnames(cum_returns_annualised_vol_yearly[6:y_dim]),"_Annualised_Volatility"))

names(cum_returns_annualised_vol_yearly_squared)[6:y_dim] = c(paste0(colnames(cum_returns_annualised_vol_yearly_squared[6:y_dim]),"_Annualised_Volatility_Squared"))

names(cum_returns_vol_capm)[6:y_dim] = c(paste0(colnames(cum_returns_vol_capm[6:y_dim]),"_IdioSyncratic_Vol_CAPM"))

names(cum_returns_vol_ff3)[6:y_dim] = c(paste0(colnames(cum_returns_vol_ff3[6:y_dim]),"_IdioSyncratic_Vol_FF3_Model"))

names(cum_returns_vol_ff4)[6:y_dim] = c(paste0(colnames(cum_returns_vol_ff4[6:y_dim]),"_IdioSyncratic_Vol_FF4_Model"))

#Join the data to obtain the final table for the Shiny App
final_joined_table = Reduce(function(...) merge(..., by='year'), list(cum_returns_beta_yearly,cum_returns_annualised_vol_yearly[,c(1,6:y_dim)],cum_returns_annualised_vol_yearly_squared[,c(1,6:y_dim)],cum_returns_vol_capm[,c(1,6:y_dim)],cum_returns_vol_ff3[,c(1,6:y_dim)],cum_returns_vol_ff4[,c(1,6:y_dim)]))

gc()
```

#Plot using Shiny App the Market Variables
```{r}

ui <- fluidPage(
  selectInput("choice", "Choose", choices = names(final_joined_table), selected = NULL),
  plotlyOutput("graph")
  )

server <- function(input, output, session){

  output$graph <- renderPlotly({
    plot_ly(final_joined_table, x = ~year, y = ~get(input$choice), type = 'scatter', mode = 'bar')
  })
}

shinyApp(ui, server)


```